---
title: "Compare MPT Analysis Approaches"
author: "Marius Barth"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
  , warning = FALSE
  , message = FALSE
)
```


## Rouder et al. (2008, Exp.1)

```{r model-and-data}
# load packages
library("hmpt")

# If you're running the analysis from an .rmd file, you only need to ensure that
# the .rmd, .eqn, and .csv files are all in the same directory.

# ------------------------------------------------------------------------------
# MPT model definition & data

EQN_FILE <- "process-dissociation.eqn"
DATA_FILE <- "rouder-2008-exp1.csv"


# if .csv format uses semicolons ";" (German format):
# data <- read.csv2(DATA_FILE, fileEncoding = "UTF-8-BOM")

# if .csv format uses commata "," (international format):
data <- read.csv(DATA_FILE, fileEncoding = "UTF-8-BOM")

# if your data does not contain category names:
colnames(data) <- 1:ncol(data) 

# take a glimpse at the data
head(data)
TreeBUGS::plotFreq(data, boxplot = FALSE, eqn = EQN_FILE)

# The experimental design did not contain a between-Ss manipulation, so the
# following code can be commented out:

# COL_ID <- "Subject"         # name of the variable encoding subject ID
# COL_CONDITION <- "ExpCond"  # name of the variable encoding group membership


# Experimental conditions should be labeled in a meaningful way. To accomplish
# this, you may want to use the `factor` function:
# unique(data[, COL_CONDITION])

# data[[COL_CONDITION]] <- factor(
#   data[[COL_CONDITION]]
#   , levels = c(1:2)
#   , labels = c("no_load", "load")
# )

### check input data frame
data$id <- 1:nrow(data)
data$condition = "no-condition"
head(data)
```

### Options

Every time the package is loaded, it automatically sets some more
or less useful defaults for model estimation, usage of multiple processor cores,
number of posterior predictive samples, etc.
By calling `mpt_options()` without any parameters, you can inspect these default values.
If you want to change them, call `mpt_options` with the respective parameter specified, i.e. `mpt_options(n.iter = 1000)`.
For testing purposes, you can also specify `mpt_options("test")`, which is a shorthand for setting fast, but highly unreliable settings.
You can set options to defaults, again, by typing the shorthand `mpt_options("default")`.

```{r options, results = 'hide'}
# How to change a single option:
mpt_options(n.iter = 1e3)

# For testing purposes, you can use this shorthand to set fast, but unreliable options:
mpt_options("test")

# List all options that were set for the different analysis approaches:
mpt_options()
```

### Estimation

In the next chunk, the main computations are done.
Type `?fit_mpt` in the R console if you want to find out more about the parameters of the function.

```{r echo = FALSE}
set.seed(42)
mpt_options("default")
```

```{r analysis, results = 'hide'}
results <- fit_mpt(
  model = EQN_FILE
  , dataset = DATA_FILE
  , data = data
  , id = "id"
  , condition = "condition"
  , core = c("c1", "c2", "c3", "a1", "a2", "a3") # Define all parameters as core
)
```

After computations finished, which may take a couple of days, check if model estimation worked by using the function `check_results`.

```{r}
check_results(results)
```

```{r echo = FALSE, eval = FALSE}
save(results, file = "results.RData")
```



### Post-processing of Results


The analysis output `results` is an object of class `multiverseMPT`, that has its own `plot()` method.
Type `?plot.multiverseMPT` to see the documentation of possible arguments to this method.

To plot group-level parameter estimates, type:

```{r}
plot(results, save = FALSE, "est")
```

To plot between-subjects comparisons, type:

```{r}
plot(results, save = FALSE, "test_between")
```

To plot overall goodness-of-fit, type:

```{r}
plot(results, save = FALSE, "gof1")
```

To plot group-wise goodness-of-fit, type:

```{r}
plot(results, save = FALSE, "gof2")
```
